Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-14 paper.qmd
Updated Figure 6

plot_predict_umap <- ggplot(data = predict_umap_scurve_scaled,
                            aes(
                              x = UMAP1,
                              y = UMAP2
                            )) +
  geom_point()
```

@@

@@

# Function to jitter points within a circumcircle of a hexagon
jitter_within_circumcircle <- function(center_x, center_y, radius, num_points) {
  theta <- runif(num_points, 0, 2 * pi)
  r <- radius * sqrt(runif(num_points))
  x <- center_x + r * cos(theta)
  y <- center_y + r * sin(theta)
  jittered_points <- data.frame(UMAP1 = x, UMAP2 = y)
  return(jittered_points)
}

@@

# Iterate through each hexagon and jitter points within the circumcircle
for (hex_id in unique(hex_grid_nonempty$hex_poly_id)) {
  hex_points <- hex_grid_nonempty %>% filter(hex_poly_id == hex_id)
  center_x <- mean(hex_points$x)
  center_y <- mean(hex_points$y)
  points_in_hex <- true_pred_df %>% filter(pred_UMAP_1 >= min(hex_points$x) & pred_UMAP_1 <= max(hex_points$x) & pred_UMAP_2 >= min(hex_points$y) & pred_UMAP_2 <= max(hex_points$y))

@@

plot_predict_umap_model <- ggplot(data = jittered_points_df,
                            aes(
                              x = UMAP1,
                              y = UMAP2
                            )) +
  geom_point()
```

@@

predict_umap_scurve_scaled <- predict_umap_scurve_scaled |>
  mutate(type = "predict_from_umap") |>
  mutate(point_id = row_number())

jittered_points_df <- jittered_points_df |>
  mutate(type = "predict_from_model") |>
  mutate(point_id = row_number())

@@

plot_predict_umap_model_connect <- ggplot(data = predict_point_df,
                            aes(
                              x = UMAP1,
                              y = UMAP2, 
                              group = point_id
                            )) +
  geom_point() +
  geom_line()
```

>>>>

plot_predict_umap <- ggplot(data = predict_umap_scurve_scaled,
                            aes(
                              x = UMAP1,
                              y = UMAP2
                            )) +
  geom_point(alpha = 0.5)
```

@@

hex_grid_nonempty <- hex_grid |>
  filter(hex_poly_id %in% df_bin_centroids_scurve$hexID)

@@

# Function to jitter points within a circumcircle of a hexagon
jitter_within_circumcircle <- function(center_x, center_y, radius, num_points) {
  theta <- runif(num_points, 0, 2 * pi)
  r <- radius * sqrt(runif(num_points))
  x <- center_x + r * cos(theta)
  y <- center_y + r * sin(theta)
  jittered_points <- data.frame(UMAP1 = x, UMAP2 = y, ID = points_in_hex$ID)
  return(jittered_points)
}

@@

# Iterate through each hexagon and jitter points within the circumcircle
for (hex_id in unique(true_pred_df$pred_hb_id)) {
  # hex_points <- hex_grid_nonempty %>% filter(hex_poly_id == hex_id)
  # center_x <- mean(hex_points$x)
  # center_y <- mean(hex_points$y)
  # points_in_hex <- true_pred_df %>% filter(pred_UMAP_1 >= min(hex_points$x) & pred_UMAP_1 <= max(hex_points$x) & pred_UMAP_2 >= min(hex_points$y) & pred_UMAP_2 <= max(hex_points$y))

  points_in_hex <- true_pred_df |>
    filter(pred_hb_id == hex_id)

  center_x <- points_in_hex |> 
    pull(pred_UMAP_1) |> 
    unique()

  center_y <- points_in_hex |> 
    pull(pred_UMAP_2) |> 
    unique()

@@

plot_predict_umap_model <- ggplot(data = jittered_points_df,
                            aes(
                              x = UMAP1,
                              y = UMAP2
                            )) +
  geom_point(alpha = 0.5)
```

@@

predict_umap_scurve_scaled <- predict_umap_scurve_scaled |>
  mutate(type = "predict_from_umap")

jittered_points_df <- jittered_points_df |>
  mutate(type = "predict_from_model")

@@

plot_predict_umap_model_connect <- ggplot(data = predict_point_df,
                            aes(
                              x = UMAP1,
                              y = UMAP2, 
                              group = ID
                            )) +
  geom_point(alpha = 0.6) +
  geom_line(alpha = 0.3)
```
